ms_figures

### 2023-02-07 ms_figures.Rmd
regional sankey by source figure

fig1a <- fig1a_data %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports (mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom")

@@

fig1b <- ggplot() +
  geom_line(data = fig1b_data, aes(x = year, y = percent_export, color = habitat_method)) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "% Production Exported", x = "", color = "Source") +
  theme_bw()

@@

fig1c_out_degree <- fig1c_data %>%
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = all_in_degree, color = habitat_method)) +
  geom_smooth() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Average no. export partners", color = "Source") + 
  theme_bw()

@@

fig1d <- ggplot() +
  geom_line(data = export_n_countries_concentration_by_source %>% 
      mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = export_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
  scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries comprising ", cumulative_percent_threshold, "% of exports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw()

@@

fig1e <- ggplot() +
  geom_line(data = import_n_countries_concentration_by_source %>% 
              mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = import_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
    scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries comprising ", cumulative_percent_threshold, "% of imports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw()

@@

```{r fig1, fig.height = 7, fig.width = 5}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          ggarrange(fig1d,
                    fig1e,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("d", "e")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 3, labels = c("a", ""))

@@

>>>>

fig1a <- fig1a_data %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports\n(mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.title.y = element_text(size = 16),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        legend.text = element_text(size = 9),
        )

@@

fig1b <- ggplot() +
  geom_line(data = fig1b_data, aes(x = year, y = percent_export, color = habitat_method)) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "% Production\nExported", x = "", color = "Source") +
  theme_bw() +
  theme(
    text = element_text(size = 16)
  )

@@

fig1c_out_degree <- fig1c_data %>%
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = all_in_degree, color = habitat_method)) +
  geom_smooth() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Average\nno. export partners", color = "Source") + 
  theme_bw() +
  theme(
    text = element_text(size = 16),
    axis.title.x = element_blank()
  )

@@

fig1d <- ggplot() +
  geom_line(data = export_n_countries_concentration_by_source %>% 
      mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = export_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
  scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries\ncomprising ", cumulative_percent_threshold, "% exports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw() +
  theme(
    text = element_text(size = 16)
  )

@@

fig1e <- ggplot() +
  geom_line(data = import_n_countries_concentration_by_source %>% 
              mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))), 
      aes(x = year, y = n, color = habitat_method)) +
  geom_line(data = import_n_countries_concentration, aes(x = year, y = n, color = "total"), linewidth = 1) +
    scale_color_manual(values = habitat_source_colors_v2) +
  labs(x = "", y = paste("No. countries\ncomprising ", cumulative_percent_threshold, "% imports", sep = ""), color = "Source") +
  lims(y = c(0, 30)) +
  theme_bw() +
  theme(
    text = element_text(size = 16)
  )

@@

```{r fig1, fig.height = 4, fig.width = 4}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          ggarrange(fig1d,
                    fig1e,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("d", "e")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 3, labels = c("a", ""))

@@

```{r regional_sankey, fig.height = 2, fig.width = 2}
# regional_artis <- read.csv(file.path(datadir, "regional_artis_by_source.csv"))
# plot_regional_sankey_method_habitat(regional_artis, 2019, 2019)

marine_cap_regions <- regional_artis %>%
  filter(habitat == "marine" & method == "capture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

marine_cap_regions$node <- factor(marine_cap_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "South America", "North America",
                                         "Africa"))

marine_cap_p <- marine_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region6_palette) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

marine_cap_p
```

```{r marine_aqua, fig.height = 2, fig.width = 2}
marine_aqua_regions <- regional_artis %>%
  filter(habitat == "marine" & method == "aquaculture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

marine_aqua_regions$node <- factor(marine_aqua_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "South America", "North America",
                                         "Africa"))

marine_aqua_p <- marine_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region6_palette) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

marine_aqua_p
```

```{r inland_cap, fig.height = 2, fig.width = 2}
inland_cap_regions <- regional_artis %>%
  filter(habitat == "inland" & method == "capture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

inland_cap_regions$node <- factor(inland_cap_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "South America", "North America",
                                         "Africa"))

inland_cap_p <- inland_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region6_palette) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

inland_cap_p
```

```{r inland_aqua, fig.height = 2, fig.width = 2}
inland_aqua_regions <- regional_artis %>%
  filter(habitat == "inland" & method == "aquaculture") %>%
  group_by(exporter_region, importer_region) %>%
    summarize(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
    ungroup() %>%
    make_long(exporter_region, importer_region, value = live_weight_t)

inland_aqua_regions$node <- factor(inland_aqua_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "South America", "North America",
                                         "Africa"))

inland_aqua_p <- inland_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region6_palette) +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(0,0,0,0), unit = "mm")
    )

inland_aqua_p
```
```{r regional_sankey_by_source, fig.height = 2.5, fig.width = 3}
ggarrange(marine_cap_p, inland_cap_p,
            marine_aqua_p, inland_aqua_p,
            ncol = 2, nrow = 2,
          labels = c("a", "b", "c", "d"))
          # labels = c("Marine Capture", "Inland Capture",
          #            "Marine Aquaculture", "Inland Aquaculture"))

ggsave(file.path(outdir, "regional_sankey_by_source.png"))
```
